
```{r}
#' ---
#' title : " Project "
#' date : 4-12-2022
#' author : Karan, Sahil,Pranava,Vidhi
```
```{r}
#'Importing packages
library(readr)
library(data.table)
library(randomForest)
library(caret)
library(rpart)
library(e1071)
library(party)
library(Epi)
library(ROCR)
library(car)
library(dplyr)
library(VIM)
library(caTools)
library(plotly)
library(scales) 
library(stringr) 
library(ggthemes) 
library(corrplot)
```

```{r}
#' Import Data
data = read_csv("C:/Users/karan/OneDrive/Desktop/IIT/Data Preparation and Analysis/Group Project/bank-full.csv")
data2 = data
head(data)
str(data)
summary(data)

#Checking dimensions of data 
dim(data)

```

```{r name-of-chunk4, fig.width=10, fig.height=4}

#' Exploratory Data Analysis
# Yes and Output Analysis

data %>% 
  count(y) %>% 
  mutate(perc = n / nrow(data)) -> predictorData2

ggplot(predictorData2, aes(x = y, y = perc)) + geom_bar(stat = "identity")
```


```{r name-of-chunk5, fig.width=10, fig.height=4}
# Job type analysis

data %>% 
  count(job) %>% 
  mutate(perc = n / nrow(data)) -> bank3

ggplot(bank3, aes(x = job, y = perc)) + geom_bar(stat = "identity")

```

```{r name-of-chunk6, fig.width=10, fig.height=4}
# Job type analysis with output field

ggplot(data, 
       aes(x = job,
           fill = y)) + 
  geom_bar(position = "dodge")

```

```{r name-of-chunk7, fig.width=10, fig.height=4}
# Marital type analysis

data %>% 
  count(marital) %>% 
  mutate(perc = n / nrow(data)) -> bank3

ggplot(bank3, aes(x = marital, y = perc)) + geom_bar(stat = "identity")
```


```{r name-of-chunk8, fig.width=10, fig.height=4}
# Marital type analysis with output field

ggplot(data, 
       aes(x = marital,
           fill = y)) + 
  geom_bar(position = "dodge")
```

```{r name-of-chunk9, fig.width=10, fig.height=4}

# Defaulter by bank field analysis 

data %>% 
  count(default) %>% 
  mutate(perc = n / nrow(data)) -> bank3

ggplot(bank3, aes(x = default, y = perc)) + geom_bar(stat = "identity")
```


```{r name-of-chunk10, fig.width=10, fig.height=4}
# Defaulter by bank analysis with output field

ggplot(data, 
       aes(x = default,
           fill = y)) + 
  geom_bar(position = "dodge")
```

# Age fieled analysis to identify age group which is contacted more by banks.

```{r name-of-chunk11, fig.width=10, fig.height=4}


data2$AgeGroup <- cut(data2$age, 
                         breaks = c(-Inf,
                                    10,20,30,40,50,60,70,80,90,100
                                    , Inf), 
                         
                         labels = c("0-9 "
                                    ,"10-19 ","20-29","30-39","40-49"
                                    ,"50-59","60-69","70-79","80-89"
                                    ,"90-100","100 +"),
                         right = FALSE)


data2 %>% 
  count(AgeGroup) %>% 
  mutate(perc = n / nrow(data2)) -> bank3

ggplot(bank3, aes(x = AgeGroup, y = perc)) + geom_bar(stat = "identity")


```

# Age fieled analysis to identify age group which is contacted more by banks with output fields
```{r name-of-chunk12, fig.width=15, fig.height=7}
ggplot(data2, 
       aes(x = AgeGroup,
           fill = y)) + 
   geom_bar(position = "dodge")
```



```{r name-of-chunk13, fig.width=10, fig.height=4}
# Housing field analysis 

data %>% 
  count(housing) %>% 
  mutate(perc = n / nrow(data)) -> bank3

ggplot(bank3, aes(x = housing, y = perc)) + geom_bar(stat = "identity")

```

```{r name-of-chunk14, fig.width=10, fig.height=4}
# Housing field analysis  with output field

ggplot(data, 
       aes(x = housing,
           fill = y)) + 
  geom_bar(position = "dodge")
```


```{r name-of-chunk15, fig.width=10, fig.height=4}
# Previous marketing outcome analysis

data %>% 
  count(poutcome) %>% 
  mutate(perc = n / nrow(data)) -> bank3

ggplot(bank3, aes(x = poutcome, y = perc)) + geom_bar(stat = "identity")
```


```{r name-of-chunk16, fig.width=10, fig.height=4}
# Previous marketing outcome  analysis with output field

ggplot(data, 
       aes(x = poutcome,
           fill = y)) + 
  geom_bar(position = "dodge")
```




# Month fields analysis shows in which month bank contact more with customers\
# Month Note- day of the week is required calculation and its not useful data as usually in any banking sector performance is calculated monthly and quarterly or yearly.

```{r name-of-chunk17, fig.width=10, fig.height=4}

data %>% 
  count(month) %>% 
  mutate(perc = n / nrow(data),Month = factor(month, levels = c("jan", "feb", "mar", "apr", "may", "jun", 
                                                                "jul", "aug", "sep", "oct", "nov", "dec"))) -> bank3

ggplot(bank3, aes(x = Month, y = perc)) + geom_bar(stat = "identity")
```

```{r name-of-chunk18, fig.width=10, fig.height=4}
# Month fields analysis shows in which month bank contact more with customers with output fields

bankMutate <- data %>%
  mutate(Month = factor(month, levels = c("jan", "feb", "mar", "apr", "may", "jun", 
                                          "jul", "aug", "sep", "oct", "nov", "dec")))

ggplot(bankMutate, 
       aes(x = Month,
           fill = y)) + 
  geom_bar(position = "dodge")
```

```{r name-of-chunk19, fig.width=10, fig.height=4}
# Call duration analysis

ggplot_duration<- ggplotly(ggplot(data, aes(x=as.factor(y), y=duration)) +
                             geom_boxplot(fill='#A4A4A4', color="black")+
                             theme_classic())
ggplot_duration

```

```{r}
#'' Data Manipulation and Descriptive Analysis
# Unique values in different columns
data%>% distinct(job)
data %>% distinct(marital)
data %>% distinct(education)
data %>% distinct(default)
data %>% distinct(loan)
data %>% distinct(contact)
data %>% distinct(poutcome)
data %>% distinct(y)


# Job Column - Spelling error
data$job<-gsub(".", "", data$job, fixed = TRUE)

# Checking missing values in data set
colSums(is.na.data.frame(data))
# No missing values in data

# Substitute unknowns in the data set with NA
data[data == "unknown"] <- NA

```


```{r}
#' Data Preparation
# Converting categorical target variable in yes/no form:
data$y<-ifelse(data$y=="yes",1,0)

```

```{r}
#' Splitting Data
set.seed(1)
# Use 70% of data set as training set and 30% as test set
sample <- sample.split(data$y, SplitRatio = 0.7)
train  <- subset(data, sample == TRUE)
test   <- subset(data, sample == FALSE)
train<-train %>% mutate(y=as.factor(y))
test<-test %>% mutate(y=as.factor(y))

# Splitting train into X and Y train
x_train<-as.data.frame(train) %>% select(-y)
y_train<-train$y
# Splitting test into X and Y train
x_test<-as.data.frame(test) %>% select(-y)
y_test<-test$y

```

```{r}
#' Imbalanced Data set
# We need to balance our data
table(y_train)

set.seed(123)
train_downsample <- downSample(x = x_train,y = y_train,yname = "y")
train_downsample<-train_downsample %>% mutate(y=as.factor(y))
```
```{r}
nume_col = c(1,6,10, 12:15)
pearson = cor(train_downsample[,nume_col])
corrplot(pearson, type = "upper")
apply(train_downsample[,nume_col],2,sd)
```

```{r}
#' Imbalanced Data set
# We need to balance our data
table(y_train)

set.seed(123)
train_downsample <- downSample(x = x_train,y = y_train,yname = "y")
train_downsample<-train_downsample %>% mutate(y=as.factor(y))

```

```{r}
#' Logistic Regression
model_full<-glm(y~.,train_downsample, family = "binomial")
summary(model_full)


# Predictions
predicted_log<-predict(model_full,x_test,type="response")
pred_log_test <- ifelse(predicted_log > 0.5, 1, 0) %>% as.factor()
cm_log<-confusionMatrix(pred_log_test,y_test,positive = "1")
cm_log

```


```{r}

#'Feature Selection 
varImp(model_full, scale = FALSE)
```

```{r}
#' Naive Bayes Classifier
model_naive <- naiveBayes(formula = y ~ duration + poutcome + pdays + month + previous , data = train_downsample,laplace=1)
summary(model_naive)

# Predictions
naive_pred = predict(model_naive,x_test,type="class" )
naive_log = confusionMatrix(table(naive_pred,y_test))
naive_log

```


